Parsing Postfix log files

### 2008-04-11 doc/logparser.tex
Improved pflogsumm section, having run it over the test log files.

    \item Pflogsumm
    \item Sawmill Universal Log File Analysis and Reporting
    \item Splunk
    \item Isoqlog
    \item Log analyser --- throughput monitor
    \item Anteater
    \item Yet Another Advanced Logfile Analyser
    \item Logparser/Lire
    \item Logrep
    \item Log Mail Analyser

@@

Pflogsumm produces a report designed for troubleshooting, rather than for
in-depth analysis.  It does not support saving any data, nor does it
extract more data than is required for producing the report.  Both the
parsing and reporting are difficult to extend as it is a specialised tool,
unlike the easily extensible design of \parsername{}.  It does not attempt
to correlate log lines by queueid or \pid{}, nor does it need to deal with
the complications encountered during this project.  Pflogsumm produces a
useful report, and successfully dealt with all the Postfix logs tested
with, but is not a suitable base for this project.

\url{http://jimsun.linxnet.com/postfix_contrib.html} \newline (Last checked
2007/08/13.)

@@

    \item The average number of mails accepted by the server per day and
        per hour.

>>>>

    \item Sawmill Universal Log File Analysis and Reporting
    \item Splunk
    \item Isoqlog
    \item Log analyser --- throughput monitor
    \item Anteater
    \item Yet Another Advanced Logfile Analyser
    \item Logparser/Lire
    \item Logrep
    \item Log Mail Analyser

@@

Pflogsumm produces a report designed for troubleshooting, rather than for
in-depth analysis.  It does not support saving any data, nor does it
extract more data than is required for producing the report.  Both the
parsing and reporting are difficult to extend as it is a specialised tool,
unlike the easily extensible design of \parsername{}.  It does not attempt
to correlate log lines by queueid or \pid{}, nor does it need to deal with
the complications encountered during this project.  Pflogsumm produces a
useful report, and successfully dealt with the \numberOFlogFILES{} logs
files tested with,\footnote{The results it reported were not verified, but
it did not report any errors, and has a very good reputation amongst
Postfix users.} but is not a suitable base for this project.

Pflogsumm's report includes the following:

    \item Total number of mails accepted, delivered and rejected.  Total
        bytes of mail accepted and delivered.

    \item Total number of sender and recipient addresses and domains.

    \item Per-hour averages and per-day summaries of the number of mails
        received, delivered, deferred, bounced and rejected.

    \item For received mail: per-domain totals for mails sent, deferred,
        average delay, maximum delay and bytes delivered.  For received
        mail: per-domain totals for mails received and bytes received.

    \item Number of mails and bytes sent and received for each address.

    \item Summary of why mail delivery was deferred or failed, why mails
        were bounced, why mails were rejected, and warning messages.

There are many options available to include or exclude certain sections of
the report.

\url{http://jimsun.linxnet.com/postfix_contrib.html} \newline (Last checked
2008/04/09.)

@@

    \item The average number of mails accepted by the server per-day and
        per-hour.
